---
title: "rl_data_analysis"
author: "Kevin Robb"
date: "10/23/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Data Analysis 10-30-2020

## Set parameters that determine which dataset will be acted on

Requires that all files for a dataset be named the same "filename" followed by "_cX" where integer X starts at 0 and increases by 1 for each additional file.

To plot a dataset, run the R chunk including the setup data for that set, and then run the R chunk under "Plot the data and save as a png."

### Q-Learning (With Reward for Reaching Goal)

```{r}
title = "Q-Learning"
filename = "q_test1_2020-10-30-18-41-09"
filedir = "q_test_data/"
num_files = 9
# define the colors we want to use for the plots. The first color will be used for the title.
colors = c("indianred", "indianred1", "indianred2", "indianred3", "indianred4", "lightsalmon1", "lightsalmon2", "lightsalmon3", "lightsalmon4")
```

### Q-Learning (No Reward for Goal)

```{r}
title = "Q-Learning (Only Negative Reward)"
filename = "q_2020-10-30-17-49-00"
filedir = "good_data/"
num_files = 6
colors = c("indianred", "indianred1", "indianred2", "indianred3", "indianred4","lightsalmon4")
```

### Double Q-Learning

```{r}
title = "Double Q-Learning"
filename = "double_q_2020-10-30-17-50-08"
filedir = "good_data/"
num_files = 6
colors = c("indianred", "indianred1", "indianred2", "indianred3", "indianred4","lightsalmon4")
```

### SARSA (No ROS)

```{r}
title = "SARSA"
filename = "sarsa_2020-10-30-17-47-33"
filedir = "good_data/"
num_files = 6
colors = c("royalblue","royalblue1","royalblue2","royalblue3","royalblue4","slateblue4")
```

### SARSA (Accelerated)

```{r}
title = "SARSA (Accelerated)"
filename = "accel_sarsa_2020-10-30-17-59-41"
filedir = "good_data/"
num_files = 6
colors = c("royalblue","royalblue1","royalblue2","royalblue3","royalblue4","slateblue4")
```

### Expected SARSA

```{r}
title = "Expected SARSA"
filename = "exp_sarsa_2020-10-30-17-48-05"
filedir = "good_data/"
num_files = 6
colors = c("royalblue","royalblue1","royalblue2","royalblue3","royalblue4","slateblue4")
```

## Plot the data and save as a png

```{r}
# put all the data in the same dataframe to use ggplot
range = c(1:24) #number of rows
df <- data.frame("episode" = range, "y" = range)
counts = c(1:num_files)
# loop through all files and store key values
for (count in counts) {
  filepath <- paste(filedir, filename, "_c", count-1, ".csv", sep="")
  print(filepath)
  df_c <- read.csv(file=filepath)
  names(df_c) <- c("episode", "steps","extra")
  # store the steps to our big dataframe
  df[count+1] = df_c$steps
}
# see the new dataframe which has all the datasets' steps as columns 2+
head(df)

# overlay all the graphs using ggplot
require(ggplot2)
# add the x values
g <- ggplot(df, aes((episode - 1)*25)) + xlim(0, 125)
# add all the sets of y values
for (count in counts) {
  g <- g + geom_line(aes_string(y=df[,count+1]), colour=colors[count])
}
# add the labels
g <- g + ylab("# of Steps to Reach Goal") + xlab("Episode")
# add the title
g <- g + ggtitle(title) + theme(plot.title=element_text(color=colors[1]))
# show the plot
g

# Save the plot to a file
# open the file
filepath = paste("plots/", filename, "_crop", ".png", sep="")
png(file=filepath, width=600, height=350)
# show the plot
g
# close the file
dev.off()
```
